---
title: "Initial analyses"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1 Data preprocessing

## 1.1 Reads in the data set that contains your dependent variable
```{r}
qs<-read.csv("qs-world-university-rankings-2017-to-2022-V2.csv")
str(qs)
```
```{r}
head(qs)
```


## 1.2 Handling missing values
```{r}
sum(!is.na(complete.cases(qs)))
```
```{r}
library(tidyverse)
#Converts missing values to NA
qs$size<-ifelse(qs$size=="",NA,qs$size)
qs$type<-ifelse(qs$type=="",NA,qs$type)
qs$research_output<-ifelse(qs$research_output=="",NA,qs$research_output)
```

## Remove the thousandth sign
```{r}
qs$international_students<-gsub(",","",qs$international_students) %>% as.integer()
qs$faculty_count<-gsub(",","",qs$faculty_count) %>% as.integer()

```



# 2 visualization

## 2.1 A univariate graphic describing the dependent variable
```{r}
library(ggplot2)
#A histogram of the distribution of scores
ggplot(qs,aes(score))+geom_histogram()
```

## 2.2 The conditional mean of your dependent variable at levels of at least one independent variable 

```{r}
#the box plot of scores of universities at different levels of study
ggplot(qs[!is.na(qs$research_output),],aes(research_output,score))+geom_boxplot(aes(fill=research_output))


```

## 2.3 The distribution of your dependent variable at levels of at least one independent variable 
```{r}
#The score density curve of universities with different campus sizes
ggplot(qs[!is.na(qs$score),],aes(score))+geom_density(aes(colour=size))
```

## 2.4 A bivariate graphic that compares your dependent variable with at least one other independent variable
```{r}
#A scatter chart of international student numbers and university ratings at different public and private universities
ggplot(qs[!is.na(qs$score),],aes(international_students,score))+geom_jitter(aes(colour=type))
```






























